\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-06 paper/paper.tex

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with pointwise confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the K-M estimate of the cdf.  With left truncation, however, the standard K-M estimator is biased, so we used an adjusted version due to\citet[Chapter 11, ]{meeker} (see Appendix for a detailed description).

@@

\subsection{Results}
\subsubsection{Model Assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the first of these.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the K-M estimate for each drive-model $g$.

>>>>

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with pointwise confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to \citet[Chapter 11]{meeker} (see Appendix for a detailed description).

@@

\subsection{Results}
\subsubsection{Model assessment}
\label{model-assessment}
Having chosen Model 4 as the best of the candidate models, we would like to assess whether our model provides an adequate description of the observed data. One way to do this is to draw replicate data sets from the posterior predictive distribution. This is a general approach recommended by \cite{gelman1996postpred} for models where no classical goodness-of-fit test is available. In the hierarchical setting, there can be different formulations of the predictive distribution. In the present context, one could predict the lifetime of a new unit of a previously observed drive-model or a new drive-model. We choose to focus on the first of these.  There are many possible approaches to the posterior predictive check. For this problem, we chose to consider the posterior predictive distribution of the K-M estimate for each drive-model $g$.
